pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single cell RNA-seq preprocessing tools

### 2020-07-02 bmc_article.tex
Updates from Overleaf

{\color{red}\textit{MCVR} and the global maximum likelihood based on translated Poisson Mixture Model (\textit{maxLikGlobal}) tended to produce clusterings with smaller deviations to the true number of subpopulations (Supplementary Figure 26). Although most methods performed well on the various clustering measures, \textit{maxLikGlobal} (using 10 or 20 nearest neighbors, although estimates were relatively stable across various values of \textit{k} -- see Supplementary Figure 27) provided the dimensionality estimate that best separated challenging subpopulations (Figure \ref{fig:dim}C) and tended to result in the best clustering accuracy (Figure \ref{fig:dim}D). \texit{MCVR} did not perform well for the datasets without UMIs (Koh and Kumar), which violate the assumptions of the method, and while it did increase the separability of some subpopulations (Figure \ref{fig:dim}C), it was detrimental to the classification of some others. We observed a strong negative correlation (\textit{r}=-0.995, p~1.6e-8) between the number of dimensions called by \textit{MCVR} and the log10 average library size of a dataset, which explained the former considerably better than the number of subpopulations.

>>>>

{\color{red} \textit{MCVR} and the global maximum likelihood based on translated Poisson Mixture Model (\textit{maxLikGlobal}) tended to produce clusterings with smaller deviations to the true number of subpopulations (Supplementary Figure 26). Although most methods performed well on the various clustering measures, \textit{maxLikGlobal} (using 10 or 20 nearest neighbors, although estimates were relatively stable across various values of \textit{k} -- see Supplementary Figure 27) provided the dimensionality estimate that best separated challenging subpopulations (Figure \ref{fig:dim}C) and tended to result in the best clustering accuracy (Figure \ref{fig:dim}D). \textit{MCVR} did not perform well for the datasets without UMIs (Koh and Kumar), which violate the assumptions of the method, and while it did increase the separability of some subpopulations (Figure \ref{fig:dim}C), it was detrimental to the classification of some others. We observed a strong negative correlation (\textit{r}=-0.995, p~1.6e-8) between the number of dimensions called by \textit{MCVR} and the log10 average library size of a dataset, which explained the former considerably better than the number of subpopulations.
